---
title: "Shiny_Final"
author: "Kaitlin Maciejewski"
date: "11/20/2017"
output: html_document
runtime: shiny
---

```{r setting up dataset, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(flexdashboard)
library(dplyr)
library(tidyr)
library(readr)
library(stringr)
library(plyr)
library(forcats)
library(tidyverse)
library(plotly)
library(janitor)
library(shiny)


us_tweets <- read_csv("us_tweets.csv") 

us_tweets$tweet_content_stripped <- gsub("[^[:alpha:] ]", "",
                                         us_tweets$tweet_content) 

us_tweets$tweet_content_stripped <- gsub(" *\\b[[:alpha:]]{1,2}\\b *", " ",
                                         us_tweets$tweet_content_stripped) 


#getting state from latitude longitude data
state_tweets = us_tweets %>%
  select("longitude", "latitude")

library(sp)
library(maps)
library(maptools)
library(gpclib)
library(stringi)

latlong2state <- function(state_tweets) {
    states <- map('state', fill=TRUE, col="transparent", plot=FALSE)
    IDs <- sapply(strsplit(states$names, ":"), function(x) x[1])
    states_sp <- map2SpatialPolygons(states, IDs=IDs,
                     proj4string=CRS("+proj=longlat +datum=WGS84"))

    states_tweets_SP <- SpatialPoints(state_tweets, 
                    proj4string=CRS("+proj=longlat +datum=WGS84"))
    
    indices <- over(states_tweets_SP, states_sp)

    stateNames <- sapply(states_sp@polygons, function(x) x@ID)
    stateNames[indices]
}


us_tweets$state_name <- stri_trans_totitle(latlong2state(state_tweets))
```

```{r, decreasing missingness}

#PARSING TO DECREASE STATE MISSINGNESS
us_tweets = us_tweets %>%
  filter(country == "US") %>%
  mutate(state = str_sub(place_as_appears_on_bio, start = -2), state = trimws(state)) 

#formatting place that was state, USA
state_fix = us_tweets %>%
  filter(state == "SA") %>%
  mutate(fixed_state = NA)


list = strsplit(state_fix$place_as_appears_on_bio, split=',', fixed=TRUE)
df <- ldply(list)
colnames(df) <- c("State", "USA")

#state name
state_fix = state_fix %>%
  mutate(state = trimws(state), fixed_state = df$State, fixed_state = trimws(fixed_state)) %>%
  mutate(fixed_state = state.abb[match(fixed_state,state.name)]) %>%
  mutate(fixed_state = state.name[match(fixed_state,state.abb)])

#add district of columbia
state_fix$fixed_state[is.na(state_fix$fixed_state)] <- "District of Columbia"

#fix SA of USA to be NA
us_tweets$state[us_tweets$state == "SA"] <- NA

#join datasets and keep most comprehensive
us_tweets = full_join(us_tweets, state_fix)%>%
  mutate(updated_state = ifelse(is.na(state), fixed_state, state)) %>%
  mutate(updated_state = state.name[match(updated_state,state.abb)]) %>%
  mutate(updated2_state = ifelse(is.na(fixed_state), updated_state,
                                 fixed_state)) %>%
  select(-state, -fixed_state, -updated_state) %>%
  mutate(final_state = ifelse(is.na(state_name), updated2_state,
                                 state_name)) %>%
  select(-state_name, -updated2_state)
  



```

```{r, further tidying}

#tidy: long form
us_tweets_long <- gather(us_tweets, key = sentiment, value = count, anger:trust, factor_key = TRUE)
 

#dataset to plot
tweets_shiny = us_tweets_long %>%
  filter(country == "US")

```

This R Markdown document is made interactive using Shiny. Unlike the more traditional workflow of creating static reports, you can now create documents that allow your readers to change the assumptions underlying your analysis and see the results immediately. 

To learn more, see [Interactive Documents](http://rmarkdown.rstudio.com/authoring_shiny.html).

## Inputs and Outputs

You can embed Shiny inputs and outputs in your document. Outputs are automatically updated whenever inputs change.  This demonstrates how a standard R plot can be made interactive by wrapping it in the Shiny `renderPlot` function. The `selectInput` and `sliderInput` functions create the input widgets used to drive the plot.

```{r sentiment by state, echo=FALSE}
which_state = tweets_shiny %>% distinct(state_name) %>% pull()


# selectInput widget
selectInput("state_choice1", label = h3("Select first state"),
            choices = which_state, selected = "New York")

renderPlotly({
    tweets_shiny %>%
    filter(count > 0, state_name == input$state_choice1)%>%
  mutate(text_label = str_c("sentiment: ", sentiment, '\nlocation: ', place_as_appears_on_bio)) %>% 
  plot_ly(x = ~longitude, y = ~latitude, type = "scatter", mode = "markers",
          alpha = 0.5, 
          color = ~sentiment, text = ~text_label)
})

```

## Embedded Application

It's also possible to embed an entire Shiny application within an R Markdown document using the `shinyAppDir` function. This example embeds a Shiny application located in another directory:

```{r tabsets, echo=FALSE}
shinyAppDir(
  system.file("examples/06_tabsets", package = "shiny"),
  options = list(
    width = "100%", height = 550
  )
)
```

Note the use of the `height` parameter to determine how much vertical space the embedded application should occupy.

You can also use the `shinyApp` function to define an application inline rather then in an external directory.

In all of R code chunks above the `echo = FALSE` attribute is used. This is to prevent the R code within the chunk from rendering in the document alongside the Shiny components.

```{r, eval= FALSE, echo= FALSE}
##CODE TO OBTAIN STATE FROM PACE AS APPEARS ON BIO

#fix location where recorded as state, USA
state_fix = tweets_shiny %>%
  filter(state == "SA") %>%
  mutate(fixed_state = NA)


list = strsplit(state_fix$place_as_appears_on_bio, split=',', fixed=TRUE)
df <- ldply(list)
colnames(df) <- c("State", "USA")

state_fix = state_fix %>%
  mutate(fixed_state = df$State) %>%
  mutate(fixed_state = state.abb[match(fixed_state,state.name)])

#join both datasets, merges states for one state column
state_fix$fixed_state[is.na(state_fix$fixed_state)] <- "DC"
tweets_shiny$state[tweets_shiny$state == "SA"] <- NA
tweets_shiny = full_join(tweets_shiny, state_fix) %>%
  mutate(state = ifelse(is.na(state), fixed_state, state)) %>%
  select(-fixed_state )

#expectation: 50 states + DC, reality: too many observations, how do we best clean up location?
length(unique(tweets_shiny$state))
unique(tweets_shiny$state)
```
